### 2023-07-19 main.tex
FCR
Dij charge
Cleaning up

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\usepackage{comment}
\usepackage{mathtools}
\usepackage{array}
\numberwithin{equation}{section}
\numberwithin{equation}{subsection}

@@

\cite{Alcaraz:1992zc} }

\cite{Sklyanin:1988yz}

@@

We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$

@@

@@

@@

	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)

@@

@@

	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I

@@

		A(x)&B_{2}(x)&\ldots&B_{N}(x)\\

@@

In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e. when the left boundary is lower triangular a end the right one is diagonal. We properly rescale them and we obtain
	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
		1+x&0&\ldots&0\\
		0&0&\ldots&1-x

@@

	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
		N+x&0&\ldots&0\\
		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
Then we obtain the correspondent transfer matrix as
	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)

@@

	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

	T^{\Delta}(x)&=tr_{0}\left(\begin{pmatrix}
		N+x&0&\ldots&0\\
		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
	\end{pmatrix}\begin{pmatrix}
	A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
\end{pmatrix}\right)\\&=
(N+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=
Q_{2L+2}x^{2L+2}+Q_{2L+1}x^{2L+1}+Q_{2L}x^{2L}+\ldots
We call these $Q_{a}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\

@@

	T_{0}(x)=(N+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)

@@

	A(x)=\sum_{a=0}^{2L+1}A^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}

@@

	A(x)=A^{2L+1}x^{2L+1}+A^{2L}x^{2L+1}+A^{2L-1}x^{2L-1}+\ldots
where .
	A^{2L+1}=I^{tot}
	A^{2L}=I^{tot}+2e_{11}^{tot}
		A^{2L-1}=3e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}

@@

We observe that $\forall i,j=1,2,\ldots,N$
\begin{equation}
	\sum_{a,b=1}^{L}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}=2e_{11}^{tot}\left(e_{11}^{tot}+I^{tot}\right)-L
\end{equation}
{\color{blue}ok?}where we used $
 \sum_{i=1}^Ne_{ii}^{tot}=L$.

While, $\forall i=2,\ldots,N$

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
	\end{split}
\end{equation}

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}=	2Ne_{ii}^{tot}+ 2e_{11}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
	\end{split}
\end{equation}
{\color{blue}ok?}
%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)}
\end{split}
\end{equation}
\begin{equation}
\begin{split}
	B_{j}^{2L-1}&=
	2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
	&=
	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

>>>>

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\usepackage{comment}
\usepackage{mathtools}
\usepackage{array}
\numberwithin{equation}{section}
\numberwithin{equation}{subsection}

@@

\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz}

@@

We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$

@@

	\widehat{K}_{0}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}
		1-x&0&\ldots&0\\
		0&0&\ldots&1+x

@@

	K_{0}=\left((2x+N)H^{''}_{left}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
		-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
		0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
		\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
		0&0&0&\ldots&0&1+x

@@

	T^{\Delta}(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)

@@

\begin{equation}\label{RURU}

@@

	\left[T^{\Delta}(x),T^{\Delta}(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T^{\Delta}(0))=C_{1}H^{''}+C_{2}I

@@

		D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\

@@

		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)

@@

The exchange relations for the elements of the above matrix can be found using \eqref{RURU}
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
		D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
\begin{equation}\label{EX2}
		D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
\begin{equation}\label{EX3}
		D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{i,i}(y)+B_{i}(y)D_{N,N}(x)\right)
		\\&-
		\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)+B_{i}(x)D_{N,N}(y)\right)
		h_{1}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}\left(B_{k}(x)D_{k,i}(y)-B_{k}(y)D_{k,i}(x)\right)

@@

	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
	\item for $j\neq N$ 
	B_{j}(x)D_{jj}(y)=&\frac{(x+y)(1+x-y)}{(x-y)(1+x+y)}D_{jj}(y)B_{j}(x)-\frac{1}{(1+x+y)}\sum_{i=1\,:\,i\neq j}^{N-1}B_{i}(x)D_{i1}(y)
	\\-&\frac{(x+y)}{(x-y)(1+x+y)}D_{jj}(x)B_{j}(y)-\frac{1}{(1+x+y)}D_{NN}(x)B_{j}(y)
\item for $i,j\neq N$
		B_{i}(x)D_{jj}(y)=D_{jj}(y)B_{j}(x)+\frac{1}{(x-y)}\left(D_{ji}(y)B_{j}(x)-D_{ji}(x)B_{j}(y)\right)
\item for $j\neq N$
		B_{j}(x)D_{NN}(y)&=\frac{(x-y)(1+x+y)}{(x+y)(1+x-y)}D_{NN}(y)B_{j}(x)+\frac{(x-y)}{(x+y)(1+x-y)}\sum_{i=1}^{N-1}B_{i}(y)D_{ij}(x)
		\frac{1}{(1+x-y)}B_{j}(y)D_{NN}(x)
%In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e. when the left boundary is lower triangular a end the right one is diagonal. We properly rescale them and we obtain

%Then, we obtain the correspondent transfer matrix as
%\begin{equation}
%	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
%\end{equation}
%where
%\begin{equation}
%	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
%\end{equation}
\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
\begin{equation}
	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\end{equation}

@@

	T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
		-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
		0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
		\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
		0&0&0&\ldots&0&1+x
	\end{pmatrix}\right.
\\& \left.
\;\;\;\begin{pmatrix}
	D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
	D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
	D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
	B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)
\end{pmatrix}\right)
Therefore we can write the polynomial expansion
		T^{\Delta}(x)=&
		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\

@@

	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)

@@

	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}

@@

	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
	D_{N,N}^{2L+1}=I^{tot}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
		D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}

@@

We observe that $\forall i,j=1,\ldots,N-1$
\begin{equation}
	\sum_{a\neq b}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	D_{N,N}^{2L-1}=e_{NN}^{tot}\left(2e_{NN}^{tot}+I^{tot}\right)-\sum_{j=1}^{N}e_{jj}^{tot}%=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}
Then
\begin{equation}
\boxed{D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L}
\end{equation}
{\color{blue}ok?}where we used $
 \sum_{i=1}^Ne_{ii}^{tot}=L$.

While, $\forall i=1,\ldots,N-1$

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
	\end{split}
\end{equation}

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}%=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
	\end{split}
\end{equation}
Then 
\begin{equation}
\boxed{D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
\end{equation}
{\color{blue}ok}
%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
	B_{j}^{2L-1}&=
	2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
Finally, for every $i,j=2,\ldots,N$ such that $i\neq j$, we have that 
\begin{equation}
	\boxed{D_{i,j}^{2L}=-2e_{ji}^{tot}}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form
